POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-07-11 challenges.tex
Improve the presentation of the final theorems in the linearity challenge.

\subsubsection{Challenge}

\begin{lemma}
  If \( \types{\Gamma}{P} \) and \( \un{T} \) then \( \types{\Cadd{\Gamma}{\hastype{x}{T}}}{P} \).
\end{lemma}

@@

\begin{theorem}
  If \( \types{\Gamma}{P} \) and \( \reduces{P}{Q} \) then \( \types{\Gamma}{Q} \).
\end{theorem}

\begin{theorem}
  If \( \types{\Cempty}{P} \) and \( \reduces{P}{Q} \) then \( Q \) is well-formed.
\end{theorem}

>>>>

\subsubsection{Challenge}
The objective of this challenge is to prove the following theorems:
\begin{theorem}
  If \( \types{\Gamma}{P} \) and \( \reduces{P}{Q} \) then \( \types{\Gamma}{Q} \).
\end{theorem}

\begin{corollary}
  If \( \types{\Cempty}{P} \) and \( \reduces{P}{Q} \) then \( Q \) is well-formed.
\end{corollary}

The following lemmas may be of use:
\begin{lemma}
  If \( \types{\Gamma}{P} \) and \( \un{T} \) then \( \types{\Cadd{\Gamma}{\hastype{x}{T}}}{P} \).
\end{lemma}

@@
